GPU-based Adaptive Beamforming for Active Sonar Imaging

### 2012-05-08 ECUA2012/gpu_capon_ecua2012.tex
la2pdf commit - 2012:05:08	04:15:29	(Tue 8.May)

Interesting to note is also that solving $\eRi\1$ remains the main bottleneck in the \gls{GPU} implementation, and it gets even worse for larger $L$'s. However, this is a general Gauss Jordan solver which does not exploit symmetry properties of $\eR$, so creating e.g.\ a batch based Cholesky solver should improve the runtimes further. Both the C and Matlab implementation in this benchmark take this symmetry into account, which partially explains why the complexity curves of these implementations are different from that of the \gls{GPU} implementation.

If the HISAS1030 was attached to a platform moving at 1.8m/s, for which the maximum range is 250\,m~\cite{Hansen2010}, the pulse repetition frequency could be set to 3\,Hz. Then the throughput required for creating critically sampled 32-beam sectorscan images in realtime would be roughly 1\,Mpixels/s. This is something our \gls{GPU} implementation could handle alone, leaving the \gls{CPU} free to take on other assignments.

@@

The authors would like to thank nVidia for providing us their unofficial linear equation batch solver, and Kongsberg Maritime and the Norwegian Defence Research Establishment (FFI) for providing us with experimental data.

>>>>

\newpage
Interesting to note is also that solving $\eRi\1$ remains the main bottleneck in the \gls{GPU} implementation, and it gets even worse for larger $L$'s. However, this is a general Gauss Jordan solver which does not exploit symmetry properties of $\eR$, so creating e.g.\ a batch based Cholesky solver should improve the runtimes further. Both the C and Matlab implementation in this benchmark take this symmetry into account, which partially explains why the complexity curves of these implementations are different from that of the \gls{GPU} implementation.

If the HISAS1030 was attached to a platform moving at 1.8m/s, for which the maximum range is 250\,m~\cite{Hansen2010}, the pulse repetition frequency could be set to 3\,Hz. Furthermore, the HISAS1030's bandwidth is 30\,kHz, so we set this to be the complex sampling frequency, and beamform $M=32$ lateral beams. The throughput required for realtime processing of these images would then be 1\,Mpixels/s. As we have seen, this is something our \gls{GPU} implementation could handle, leaving the \gls{CPU} free to take on other assignments.

@@

The authors would like to thank nVidia for providing them their unofficial linear equation batch solver, and Kongsberg Maritime and the Norwegian Defence Research Establishment (FFI) for providing experimental data.
